Effects of rotation and magnetic braking on Li abundances for solar-type stars

### 2019-07-09 project/overleaf/paper.tex
Paper v3.0
Improve graphs quality

The mass of stars plays a determining role in the existence or not of an external convective envelope. In turn, the presence of this convective region conditions the evolution of magnetic fields. As depicted in figure (\ref{fig:hr_hussain}), massive stars do not have external convective zones although they can expose a convective core. In these cases, the dominant type of energy transport in the outer zones of the star is radiative. On the other hand, the less massive stars, such as those of the solar-type, have convective covers and radiative core. In both types of stars strong magnetic fields can be generated in the limits of both zones (the so-called tachocline) but with notable differences. In the case of massive stars, these magnetic fields can survive for a long time but not reach the surface of the star. On the other hand in less massive stars these magnetic fields, although they are able to reach the surface of the star, decay quickly in time, in a few hundred years or even only in a few decades \citep{Chabrier2006}, so it is necessary a mechanism for generating magnetic field, e.g. a dynamo type, continued in time to explain its existence. The way in which this dynamo process is able to generate magnetic fields depends on different parameters and to this day this mechanism is still not fully accepted and is subject of controversy, e.g. \citep{Charbonneau2010}.\par

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/hussain_gaitee_fig1.png}
    \caption{H-R diagram showing PMS evolutionary tracks for stars with masses up to $4.0 \; M_{\sun}$. The dashed blue line marks the position of the birthline. The stars with $1.0 \; M_{\sun}$ which have a fully convective interior near the Hayashi track, they will to develop a radiative core when they're approaching the ZAMS (black dot-dashed line). Image copied from \citet{Hussain2014}}
    \label{fig:hr_hussain}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/li_var_vel_0_0g.eps}
    \caption{The evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. The solid black line represents the reference model according to \citet{Choi2016}. The rest of lines are models which include PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS defined as the temporal simulation instant closest to the timestep in which both the central H mass fraction has been reduced by 0.0015 from its initial value and the model first $L_H/L_{phot} \geq 0.99$, where $L_{H}$ is luminosity produced by the H burning power at the star core and $L_{phot}$ represents the star luminosity in the photosphere.}
    \label{fig:li_var_vel_0g}
\end{figure}

@@

The figure (\ref{fig:li_var_vel_0g}) clearly allows to appreciate how the Li abundance in the star surface decreases over time for all simulated models. The solid black line represents the reference model that adopts the solar-calibrated envelope overshooting parameters as documented in \citet{Choi2016}. In general, all models burn too much Li early on and do not match with the Pleiades surface Li abundance. Later, the reference model (black line) does not deplete Li efficiently on the MS and fail (again) to match the current solar surface Li abundance. On the other hand, the other models which include rotation during the PMS with values of $v/v_{crit}$ between 0.0084 and 0.0336 are able to burn Li in a more realistic way although only one of them (green line) is close to match the present-day Li abundance of the Sun but it rotational velocity is much higher (see fig. (\ref{fig:rot_vel_0g})) than the $2\,kms^{-1}$ of the Sun \citep{Gill2012}. \par

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/li_var_vel_0_0g_z1.eps}
    \caption {The evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models in the approach to the ZAMS (dashed lines). The solid black line represents the reference model according to \citet{Choi2016}. The rest of lines are models with includes PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively.}
    \label{fig:li_var_vel_0g_z1}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/rot_vel_0g.eps}
    \caption{The evolution of surface rotational velocity, as a function of time for several 1 $M_{\sun}$ models. The lines are models with includes PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. The purple star is the surface angular velocity for the present-day Sun \citep{Gill2012}. The dashed lines make reference to the ZAMS.}
    \label{fig:rot_vel_0g}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/rot_vel_cz_0g.eps}
    \caption{The evolution of angular velocity at surface and limits of the uppermost convective zone, as a function of time for several 1 $M_{\sun}$ models. The lines are models with includes PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. The purple star is the surface angular velocity for the present-day Sun \citep{Gill2012}. The dashed lines make reference to the ZAMS.}
    \label{fig:rot_vel_cz_0g}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/hr_var_vel_0g.eps}
    \caption{An example solar 1$M_{\sun}$ grid of stellar evolutionary track from PMS till TAMS covering a wide range of angular velocities. The rotation is activated in the models in the PMS.}
    \label{fig:hr_var_vel_0g}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/hr_var_vel_0g_z1.eps}
    \caption{Similar to figure (\ref{fig:hr_var_vel_0g}) but now showing in detail the effects of rotation on the evolutionary tracks.}
    \label{fig:hr_var_vel_0g_z1}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/li_var_vel_4_0g.eps}
    \caption{The evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. The models include a magnetic field with an intensity of 4G and PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS.}
    \label{fig:li_var_vel_4_0g}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/rot_vel_4g.eps}
    \caption{The evolution of surface rotational velocity, as a function of time for several 1 $M_{\sun}$ models. The models include a magnetic field with an intensity of 4G and PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. Additionally it's simulated the magnetic braking effect of magnetic field with an intensity of 4G. The purple star is the surface angular velocity for the present-day Sun \citep{Gill2012}. The dashed lines make reference to the ZAMS.}
    \label{fig:rot_vel_4g}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/rot_vel_cz_4g.eps}
    \caption{The evolution of angular velocity at surface and limits of the uppermost convective zone, as a function of time for several 1 $M_{\sun}$ models. The lines are models with includes PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. The dashed lines make reference to the ZAMS.}
    \label{fig:rot_vel_cz_4g}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/rot_vel_4g_z1.eps}
    \caption{Similar to figure (\ref{fig:rot_vel_4g}) but now showing in detail the surface rotational velocity as the star approaches TAMS.}
    \label{fig:rot_vel_4g_z1}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/cz_vc_028_var_b.eps}
    \caption{The evolution of convective zone size, as a function of time for several 1 $M_{\sun}$ models. The models include a magnetic field with an intensity of 4G and PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. Additionally it's simulated the magnetic braking effect of magnetic field with an intensity of 4G.The dashed lines make reference to the ZAMS.}
    \label{fig:cz_vc_028_var_b}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/cz_vc_028_var_b_z1.eps}
    \caption{Similar to figure (\ref{fig:cz_vc_028_var_b}) but now showing in detail the convection zone size from the near ZAMS till the TAMS. As the intensity of the magnetic field increases, the size of the convective zone decreases.}
    \label{fig:cz_vc_028_var_b_z1}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/mdot_vc_028_var_b.eps}
    \caption{The evolution of mass loss $\Dot{M}$ , as a function of time for several 1 $M_{\sun}$ models. The models include a variable magnetic field intensity between 0G and 5.5G and PMS rotation with $v/v_{crit}=0.028$. The dashed lines make reference to the ZAMS.}
    \label{fig:mdot_vc_028_var_b}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/mdot_vc_028_var_b_z1.eps}
    \caption{The evolution of mass loss $\Dot{M}$ as the star is approaching TAMS, as a function of time for several 1 $M_{\sun}$ models. The models include a variable magnetic field intensity between 0G and 5.5G and PMS rotation with $v/v_{crit}=0.028$. The stronger the magnetic field, the lower both the angular velocity and $\Dot{M}$. The dashed lines make reference to the ZAMS.}
    \label{fig:mdot_vc_028_var_b_z1}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/mb_act_var_vel_vc_028.eps}
    \caption{The activation of the magnetic braking routine as a function of the presence of a radiative core. The models include a magnetic field with an intensity of 4G and PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. Additionally it's simulated the magnetic braking effect of magnetic field with an intensity of 4G. The solid lines signal the magnetic braking routine activation (on) and deactivation (off). The horizontal dashed lines inform about the star's core nature: radiative (rad) or convective (conv). By implementation decision, once the routine is activated, it remains on even if the star's core nature change to convective. The vertical dashed lines make reference to the ZAMS.}
    \label{fig:mb_act_var_vel_vc_028}
\end{figure}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_var_vel_0_0g.eps}
    \label{fig:subim1}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_var_vel_3_5g.eps}
    \label{fig:subim2}
    \end{subfigure}

    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_var_vel_4_0g.eps}
    \label{fig:subim3}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_var_vel_4_5g.eps}
    \label{fig:subim4}
    \end{subfigure}

    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_var_vel_5_0g.eps}
    \label{fig:subim5}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_var_vel_5_5g.eps}
    \label{fig:subim6}
    \end{subfigure}
\caption{Grid showing the evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. Each figure shows a set of models in which the magnetic field with intensity has been fixed and $v/v_{crit}$ varies between 0.0084 and 0.0336, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS defined as the temporal simulation instant closest to the timestep in which both the central H mass fraction has been reduced by 0.0015 from its initial value and the model first $L_H/L_{phot} \geq 0.99$, where $L_{H}$ is luminosity produced by the H burning power at the star core and $L_{phot}$ represents the star luminosity in the photosphere.}
\label{fig:image2}
\end{figure*}
\par

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_vc_0084_var_b.eps}
    \label{fig:subim21}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_vc_014_var_b.eps}
    \label{fig:subim22}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_vc_0196_var_b.eps}
    \label{fig:subim23}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_vc_028_var_b.eps}
    \label{fig:subim24}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_vc_0336_var_b.eps}
    \label{fig:subim25}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/blank.eps}
    \label{fig:subim26}
    \end{subfigure}
\caption{Grid showing the evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. Each figure shows a set of models in which $v/v_{crit}$ has been fixed and the magnetic field with intensity varies between 3.5 and 5.5 G, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS defined as the temporal simulation instant closest to the timestep in which both the central H mass fraction has been reduced by 0.0015 from its initial value and the model first $L_H/L_{phot} \geq 0.99$, where $L_{H}$ is luminosity produced by the H burning power at the star core and $L_{phot}$ represents the star luminosity in the photosphere.}
\label{fig:image22}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/rot_vel_0g.eps}
    \label{fig:subim41}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/rot_vel_3_5g.eps}
    \label{fig:subim42}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/rot_vel_4g.eps}
    \label{fig:subim43}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/rot_vel_4_5g.eps}
    \label{fig:subim44}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/rot_vel_5g.eps}
    \label{fig:subim45}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/rot_vel_5_5g.eps}
    \label{fig:subim46}
    \end{subfigure}
\caption{Grid showing the evolution of the evolution of surface rotational velocity, as a function of time for several 1 $M_{\sun}$ models. Each figure shows a set of models in which the magnetic field with intensity has been fixed and $v/v_{crit}$ varies between 0.0084 and 0.0336. The purple star is the surface angular velocity for the present-day Sun \citep{Gill2012}. The dashed lines make reference to the ZAMS defined as the temporal simulation instant closest to the timestep in which both the central H mass fraction has been reduced by 0.0015 from its initial value and the model first $L_H/L_{phot} \geq 0.99$, where $L_{H}$ is luminosity produced by the H burning power at the star core and $L_{phot}$ represents the star luminosity in the photosphere.}
\label{fig:image24}
\end{figure*}

>>>>

The mass of stars plays a determining role in the existence or not of an external convective envelope. In turn, the presence of this convective region conditions the evolution of magnetic fields. Massive stars do not have external convective zones although they can expose a convective core. In these cases, the dominant type of energy transport in the outer zones of the star is radiative. On the other hand, the less massive stars, such as those of the solar-type, have convective covers and radiative core. In both types of stars strong magnetic fields can be generated in the limits of both zones (the so-called tachocline) but with notable differences. In the case of massive stars, these magnetic fields can survive for a long time but not reach the surface of the star. On the other hand in less massive stars these magnetic fields, although they are able to reach the surface of the star, decay quickly in time, in a few hundred years or even only in a few decades \citep{Chabrier2006}, so it is necessary a mechanism for generating magnetic field, e.g. a dynamo type, continued in time to explain its existence. The way in which this dynamo process is able to generate magnetic fields depends on different parameters and to this day this mechanism is still not fully accepted and is subject of controversy, e.g. \citep{Charbonneau2010}.\par

@@

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip, width=\columnwidth]{figures/li_var_vel_0_0g.eps}
    \caption{The evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. The solid black line represents the reference model according to \citet{Choi2016}. The rest of lines are models which include PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS.}
    \label{fig:li_var_vel_0g}
\end{figure}

@@

The figure (\ref{fig:li_var_vel_0g}) clearly allows to appreciate how the Li abundance in the star surface decreases over time for all simulated models. The solid black line represents the reference model that adopts the solar-calibrated envelope overshooting parameters as documented in \citet{Choi2016}. In general, all models burn too much Li before the ZAMS \footnote{Defined as the temporal simulation instant closest to the timestep in which both the central H mass fraction has been reduced by 0.0015 from its initial value and the model first $L_H/L_{phot} \geq 0.99$, where $L_{H}$ is luminosity produced by the H burning power at the star core and $L_{phot}$ represents the star luminosity in the photosphere.} and do not match with the Pleiades surface Li abundance. Later, the reference model (black line) does not deplete Li efficiently on the MS and fail (again) to match the current solar surface Li abundance. On the other hand, the other models which include rotation during the PMS with values of $v/v_{crit}$ between 0.0084 and 0.0336 are able to burn Li in a more realistic way although only one of them (green line) is close to match the present-day Li abundance of the Sun but it rotational velocity is much higher (see fig. (\ref{fig:rot_vel_0g})) than the $2\,kms^{-1}$ of the Sun \citep{Gill2012}. \par

@@

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/li_var_vel_0_0g_z1.eps}
    \caption {The evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models in the approach to the ZAMS (dashed lines). The solid black line represents the reference model according to \citet{Choi2016}. The rest of lines are models with includes PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively.}
    \label{fig:li_var_vel_0g_z1}
\end{figure}

@@

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/rot_vel_var_vel_0_0g.eps}
    \caption{The evolution of surface rotational velocity, as a function of time for several 1 $M_{\sun}$ models. The lines are models with includes PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. The purple star is the surface angular velocity for the present-day Sun \citep{Gill2012}. The dashed lines make reference to the ZAMS.}
    \label{fig:rot_vel_0g}
\end{figure}

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/rot_vel_var_vel_0_0g.eps}
    \caption{The evolution of angular velocity at surface and limits of the uppermost convective zone, as a function of time for several 1 $M_{\sun}$ models. The lines are models with includes PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. The purple star is the surface angular velocity for the present-day Sun \citep{Gill2012}. The dashed lines make reference to the ZAMS.}
    \label{fig:rot_vel_cz_0g}
\end{figure}
%\includegraphics[trim = 35mm 95mm 40mm 100mm, clip, width=0.475\textwidth]

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/hr_vc_0336_var_g_z1.eps}
    \caption{An example solar 1$M_{\sun}$ grid of stellar evolutionary track from PMS till TAMS covering a wide range of angular velocities. The rotation is activated in the models in the PMS.}
    \label{fig:hr_var_vel_0g}
\end{figure}

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/hr_var_vel_0_0g_z1.eps}
    \caption{Similar to figure (\ref{fig:hr_var_vel_0g}) but now showing in detail the effects of rotation on the evolutionary tracks.}
    \label{fig:hr_var_vel_0g_z1}
\end{figure}

@@

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/li_var_vel_4_0g.eps}
    \caption{The evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. The models include a magnetic field with an intensity of 4G and PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS.}
    \label{fig:li_var_vel_4_0g}
\end{figure}

@@

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/rot_vel_var_vel_4_0g.eps}
    \caption{The evolution of surface rotational velocity, as a function of time for several 1 $M_{\sun}$ models. The models include a magnetic field with an intensity of 4G and PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. Additionally it's simulated the magnetic braking effect of magnetic field with an intensity of 4G. The purple star is the surface angular velocity for the present-day Sun \citep{Gill2012}. The dashed lines make reference to the ZAMS.}
    \label{fig:rot_vel_4g}
\end{figure}

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/rot_vel_var_vel_4_0g.eps}
    \caption{The evolution of angular velocity at surface and limits of the uppermost convective zone, as a function of time for several 1 $M_{\sun}$ models. The lines are models with includes PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. The dashed lines make reference to the ZAMS.}
    \label{fig:rot_vel_cz_4g}
\end{figure}

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/rot_vel_var_vel_4_0g_z1.eps}
    \caption{Similar to figure (\ref{fig:rot_vel_4g}) but now showing in detail the surface rotational velocity as the star approaches TAMS.}
    \label{fig:rot_vel_4g_z1}
\end{figure}

@@

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/cz_vc_028_var_g.eps}
    \caption{The evolution of convective zone size, as a function of time for several 1 $M_{\sun}$ models. The models include a magnetic field with an intensity of 4G and PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. Additionally it's simulated the magnetic braking effect of magnetic field with an intensity of 4G.The dashed lines make reference to the ZAMS.}
    \label{fig:cz_vc_028_var_b}
\end{figure}

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/cz_vc_028_var_g_z1.eps}
    \caption{Similar to figure (\ref{fig:cz_vc_028_var_b}) but now showing in detail the convection zone size from the near ZAMS till the TAMS. As the intensity of the magnetic field increases, the size of the convective zone decreases.}
    \label{fig:cz_vc_028_var_b_z1}
\end{figure}

@@

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/mdot_vc_028_var_g.eps}
    \caption{The evolution of mass loss $\Dot{M}$ , as a function of time for several 1 $M_{\sun}$ models. The models include a variable magnetic field intensity between 0G and 5.5G and PMS rotation with $v/v_{crit}=0.028$. The dashed lines make reference to the ZAMS.}
    \label{fig:mdot_vc_028_var_b}
\end{figure}

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/mdot_vc_028_var_g_z1.eps}
    \caption{The evolution of mass loss $\Dot{M}$ as the star is approaching TAMS, as a function of time for several 1 $M_{\sun}$ models. The models include a variable magnetic field intensity between 0G and 5.5G and PMS rotation with $v/v_{crit}=0.028$. The stronger the magnetic field, the lower both the angular velocity and $\Dot{M}$. The dashed lines make reference to the ZAMS.}
    \label{fig:mdot_vc_028_var_b_z1}
\end{figure}

\begin{figure}
	\includegraphics[trim = 40mm 15mm 15mm 15mm, clip,width=\columnwidth]{figures/mb_act_vc_028_var_g.eps}
    \caption{The activation of the magnetic braking routine as a function of the presence of a radiative core. The models include a magnetic field with an intensity of 4G and PMS rotation with $v/v_{crit}$ between 0.0084 and 0.0336, respectively. Additionally it's simulated the magnetic braking effect of magnetic field with an intensity of 4G. The solid lines signal the magnetic braking routine activation (on) and deactivation (off). The horizontal dashed lines inform about the star's core nature: radiative (rad) or convective (conv). By implementation decision, once the routine is activated, it remains on even if the star's core nature change to convective. The vertical dashed lines make reference to the ZAMS.}
    \label{fig:mb_act_var_vel_vc_028}
\end{figure}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_0_0g.eps}
    \label{fig:subim1}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_3_5g.eps}
    \label{fig:subim2}
    \end{subfigure}

    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_4_0g.eps}
    \label{fig:subim3}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_4_5g.eps}
    \label{fig:subim4}
    \end{subfigure}

    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_5_0g.eps}
    \label{fig:subim5}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_5_5g.eps}
    \label{fig:subim6}
    \end{subfigure}
\caption{Grid showing the evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. Each figure shows a set of models in which the magnetic field with intensity has been fixed and $v/v_{crit}$ varies between 0.0084 and 0.0336, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS.}
\label{fig:image2}
\end{figure*}
\par

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_0084_var_g.eps}
    \label{fig:subim21}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_014_var_g.eps}
    \label{fig:subim22}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_0196_var_g.eps}
    \label{fig:subim23}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_028_var_g.eps}
    \label{fig:subim24}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_0336_var_g.eps}
    \label{fig:subim25}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/blank.eps}
    \label{fig:subim26}
    \end{subfigure}
\caption{Grid showing the evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. Each figure shows a set of models in which $v/v_{crit}$ has been fixed and the magnetic field with intensity varies between 3.5 and 5.5 G, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS.}
\label{fig:image22}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/rot_vel_var_vel_0_0g.eps}
    \label{fig:subim41}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/rot_vel_var_vel_3_5g.eps}
    \label{fig:subim42}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/rot_vel_var_vel_4_0g.eps}
    \label{fig:subim43}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/rot_vel_var_vel_4_5g.eps}
    \label{fig:subim44}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/rot_vel_var_vel_5_0g.eps}
    \label{fig:subim45}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/rot_vel_var_vel_5_5g.eps}
    \label{fig:subim46}
    \end{subfigure}
\caption{Grid showing the evolution of the evolution of surface rotational velocity, as a function of time for several 1 $M_{\sun}$ models. Each figure shows a set of models in which the magnetic field with intensity has been fixed and $v/v_{crit}$ varies between 0.0084 and 0.0336. The purple star is the surface angular velocity for the present-day Sun \citep{Gill2012}. The dashed lines make reference to the ZAMS.}
\label{fig:image24}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/mb_act_var_vel_3_5g.eps}
    \label{fig:subim31}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/mb_act_var_vel_4_0g.eps}
    \label{fig:subim32}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/mb_act_var_vel_4_5g.eps}
    \label{fig:subim33}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/mb_act_var_vel_5_0g.eps}
    \label{fig:subim34}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/mb_act_var_vel_5_5g.eps}
    \label{fig:subim35}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/blank.eps}
    \label{fig:subim36}
    \end{subfigure}
\caption{Grid showing the evolution of magnetic braking activation, as a function of time and the existence of a radiative core for several 1 $M_{\sun}$ models. Each figure shows a set of models in which the magnetic field with intensity has been fixed and $v/v_{crit}$ varies between 0.0084 and 0.0336. The dashed lines make reference to the ZAMS.}
\label{fig:image32}
\end{figure*}
